Manuscript Figures for Genome Biology (simulation subset)

### 2018-09-13 manuscript_figures/manuscript_figures_sims.Rmd
Add sim plot of unimodal effects with 25percent nonnull

methodset <- c("bonf", "bh", "ihw", "qvalue", "bl-df03", "lfdr",
               "fdrreg-e", "fdrreg-t", "ashq", "adapt-glm")
```

@@

>>>>

methodset <- c("bonf", "bh", "ihw", "qvalue", "bl", "lfdr",
               "fdrreg-e", "fdrreg-t", "ashq", "adapt-glm")
```

@@

# Supplementary Figure (unimodal assumption, 25% non-null)

This is a faceted figure with results from the pure simulation studies investigating the behavior of methods acorss different sampling distributions of the effect size for non-null tests, similar to Supplementary Figure S2 above. However, in contrast to the above simulation settings where only 10% of the hypotheses were non-null, these simulations were performed with a higher percentage (25%) of non-null tests. Again, the distributions of effect sizes used were taken from the Stephens (Biostatistics, 2016) paper, with all effect sizes doubled.

As with the AdaPT simulations above, since these results are not included in the primary set of simulation results summarized in the `resmet` object, we recompute them from the output of the `supplementary/simulations-uasettings-nonnull25.Rmd` simulation case study.

```{r SFigureS5-parse-data}
ua25files <- list.files(file.path("..", "datasets", "simulations", "supplementary", "results"),
                        "uasettings-25-benchmark", full.names = TRUE)

ua25 <- lapply(ua25files, readRDS)

ua25_i <- lapply(ua25, lapply, `[[`, "informative")
ua25_i <- lapply(ua25_i, plotsim_standardize, alpha = seq(0.01, 0.10, 0.01))
names(ua25_i) <- gsub("uasettings-25-benchmark-(.*?)\\.rds", "\\1", basename(ua25files))
ua25_i <- bind_rows(ua25_i, .id = "signal")
ua25_i <- dplyr::select(ua25_i, signal, rep, blabel, param.alpha, key, performanceMetric, alpha, value)

ua25_u <- lapply(ua25, lapply, `[[`, "uninformative")
ua25_u <- lapply(ua25_u, plotsim_standardize, alpha = seq(0.01, 0.10, 0.01))
names(ua25_u) <- gsub("uasettings-25-benchmark-(.*?)\\.rds", "\\1", basename(ua25files))
ua25_u <- bind_rows(ua25_u, .id = "signal")
ua25_u <- dplyr::select(ua25_u, signal, rep, blabel, param.alpha, key, performanceMetric, alpha, value)

ua25 <- dplyr::full_join(ua25_i, ua25_u,
                              by = c("signal", "rep", "blabel", "param.alpha", "performanceMetric", "alpha"),
                              suffix = c(".info", ".uninfo"))

## clean up IHW methods
ua25 <- dplyr::filter(ua25, !grepl("ihw-", blabel) | param.alpha == as.character(alpha))
ua25 <- dplyr::mutate(ua25, blabel = ifelse(grepl("ihw-", blabel), "ihw", blabel))
ua25 <- dplyr::mutate(ua25, blabel = ifelse(blabel == "bl-df03", "bl", blabel))
ua25 <- dplyr::rename(ua25, Method = blabel, key = performanceMetric)
ua25 <- dplyr::select(ua25, -param.alpha)
ua25 <- dplyr::mutate(ua25, Method = factor(Method, levels = methodset))
ua25 <- dplyr::filter(ua25, !is.na(Method))

ua25met <- dplyr::mutate(ua25,
                         value.info = ifelse(is.na(value.info) & grepl("R$", key), 0, value.info),
                         value.uninfo = ifelse(is.na(value.uninfo) & grepl("R$", key), 0, value.uninfo))

ua25met <- dplyr::group_by(ua25met, Method, signal, key, alpha)
ua25met <- dplyr::summarize(ua25met,
                            mean.info = mean(value.info, na.rm = TRUE),
                            se.info = sd(value.info, na.rm = TRUE) / sqrt(sum(!is.na(value.info))),
                            nNA.info = sum(is.na(value.info)),
                            mean.diff = mean(value.info - value.uninfo, na.rm = TRUE),
                            se.diff = sd(value.info - value.uninfo, na.rm = TRUE) /
                                sqrt(sum(!is.na(value.info - value.uninfo))))
ua25met <- dplyr::ungroup(ua25met)
```

After computing the performance metrics, we now plot the results for all methods. Again, we plot the mean FDR and TPR at nominal FDR cutoffs of 0.01 to 0.10 across 100 replications, as well as the FDR and TPR differences with and without the informative covariate.

```{r SFigureSim5, fig.width = 8, fig.height = 6}
## SFigure Sim5 B,C: FDR/TPR of methods across unimodal effect size distribution
ps5b <- genplot(ua25met, cov = alpha, met = "FDR") +
    facet_grid(. ~ signal, labeller = label_parsed) +
    scale_x_continuous(breaks = seq(0, .1, .02)) +
    expand_limits(x = 0)
ps5c <- genplot(ua25met, cov = alpha, met = "TPR") +
    facet_grid(. ~ signal, labeller = label_parsed) +
    scale_x_continuous(breaks = seq(0, .1, .02)) +
    expand_limits(x = 0)

## SFigure Sim5 D,E: FDR/TPR difference of methods
ps5d <- genplot(ua25met, cov = alpha, type = "diff", met = "FDR") +
    facet_grid(. ~ signal, labeller = label_parsed) +
    scale_x_continuous(breaks = seq(0, .1, .02)) +
    expand_limits(x = 0) +
    ylab(expression(paste("Mean ", Delta, "FDR (informative-uninformative)")))
ps5e <- genplot(ua25met, cov = alpha, type = "diff", met = "TPR") +
    facet_grid(. ~ signal, labeller = label_parsed) +
    scale_x_continuous(breaks = seq(0, .1, .02)) +
    expand_limits(x = 0) +
    ylab(expression(paste("Mean ", Delta, "TPR (informative-uninformative)")))

## create title for SFigure Sim5
ps5Title <- ggdraw() +
    draw_label("Simulation performance across unimodal effect size distributions w/ 25% non-null",
               fontface = 'bold', size = 15)

## pull SFigure Sim5 together
SFigS5 <- plot_grid(ps2a + guides(color = FALSE, linetype = FALSE),
                    ps5b + guides(color = FALSE, linetype = FALSE),
                    ps5c + guides(color = FALSE, linetype = FALSE),
                    ps5d + guides(color = FALSE, linetype = FALSE),
                    ps5e + guides(color = FALSE, linetype = FALSE),
                    labels = LETTERS[1:5], ncol = 1, rel_heights = c(.6, rep(1, 4)))
SFigS5 <- plot_grid(ps5Title, SFigS5, ncol = 1, rel_heights = c(0.03, 1))
SFigS5 <- plot_grid(SFigS5, get_legend(ps5b), rel_widths = c(6.5, 1))
SFigS5
ggsave(file.path(outdir, "SFigureSim5.pdf"), width=12, height=16)
```
